% 0. Abstract
\chapter*{Abstract}

This report describes the compiled project of Group 1 regarding the course PRJ3, which is the semester-project of the 3rd semester at ASE. The project is, through the project-assignment paper\footcite{prj3-oplaeg}, required to contain operators, a user interface, topics from other courses, embedded Linux and a PSoC platform.

The chosen project formulation is the development of an automatic lamp-crane-system ‘L.A.M.P.’ that will enable the lamps position to be easily customized. The crane-structure will be placed under the ceiling in a room and will be controlled from an accessible user interface by means of a Devkit8000 touchscreen. The lamp will be able to be moved in 3 dimensions: An X- and Y-axis (along and across the room) and a Z-axis (at height). The lamp is able to be positioned freely in a limited 3-dimensional space. 3 different types of sensors will also respectively detect the brightness in the room, the distance from the lamp down to nearest obstacle and whether there is any movement in the room or not.

The Project is completed trough the ASE-model\footcite{udviklingVejledning} and a prototype has been designed, constructed and implemented. The subtopics of the project, that is, Project formulation, Requirements-specifications, design and implementation are created iteratively.

A series of Acceptance-tests of the functionality for L.A.M.P is conducted and completed\footcite{documentation} in order to ensure the total system is operational and works as intended.